---
title: "PSTAT 274 Project"
author: "Carlos Baez"
date: "November 20, 2018"
output:
  html_document: default
  pdf_document: default
  word_document: default
---
#Set-up
```{r setup, include=FALSE}
library(tidyverse)
library(lubridate)
library(stats)
library(urca)
library(car)
library(forecast)
require(MASS)
library(dplyr)
library(AICcmodavg)
Rides_DataA <- read_csv("Rides_DataA.csv")
```

```{r clean-data}
#Generate CSV to Explore with Kepler.GL
longrides <- filter(Rides_DataA, distance_travelled >= 50000) %>% dplyr::select(start_location_lat, start_location_long, end_location_lat, end_location_long, distance_travelled)
write.csv(longrides, "longrides.csv")

#Filter out data with more than 100,000 m in distance_travelled
Trip_Data <-filter(Rides_DataA, distance_travelled <= 100000) %>% dplyr::select(start_location_lat, start_location_long, end_location_lat, end_location_long, distance_travelled, started_on, completed_on)
rm(Rides_DataA)
```

```{r make-time-series}
#Hourly 
Trip_hourly <- Trip_Data %>% mutate(day = as.numeric(date(started_on)), wday = wday(started_on), hour = hour(started_on)) %>% group_by(day, wday, hour) %>% summarize(count = n())

#Get Hours where count is zero
full_dates <- cbind(rep(16956:17269,each=24),seq(0,23))
full_dates <-as.data.frame(full_dates)
full_dates <- full_dates %>% mutate(wday = wday(as_date(V1)))
Trip_hourly <- full_join(Trip_hourly,full_dates, by = c("day" = "V1", "wday" ="wday", "hour"= "V2"))
Trip_hourly <- arrange(Trip_hourly, day, hour) %>% mutate(count = ifelse(is.na(count), 0, count))
write.csv(Trip_hourly,"trip_hourly.csv")
rm(full_dates)

#Make time series
trip_H <- ts(Trip_hourly)[,4]
```

```{r functions}
sarima.can <- function(ts.model, a.vector, o.vector, season.f){
  out <- tryCatch(
    #Try
    withCallingHandlers( 
     {
      #Run model
        arima(ts.model, order = a.vector, seasonal = list(order = o.vector, period = season.f), optim.method="Nelder-Mead")
      },
    
      #Warning
        warning = function(warn){
          invokeRestart("muffleWarning")
       }
      ),
    
    #Error
      error = function(err){
        return(NA)
      }
  )
  return(out)
}
```

#Exploring Data
```{r explore-std, echo=FALSE}

#Time Series Stats
  png("tspolt_trip_H.png") 
  plot.ts(trip_H, xlab = "Time (Hour)", ylab = "Trip Count", main = "Hourly Trips provided by RideAustin June 2016 - August 2017")
  dev.off()
  
  #Summary Stats
  ts_mean <- mean(trip_H) 
  ts_var <- var(trip_H)
  
  #Decomposition plot
    #Daily
    seasonplot(trip_H, 24, col = rainbow(3), year.labels=TRUE, main="Seasonal Plot - Daily")
  
    #Weekly
    seasonplot(trip_H, 168, col = rainbow(3), year.labels=TRUE, main="Seasonal Plot - Weekly")
    
  #Seasonal Trends
    trips.trend.24 <- ma(trip_H, order = 24, centre = T)
    trips.trend.168 <- ma(trip_H, order = 168, centre = T)
    plot(as.ts(trips.trend.24), col ="blue")
    lines(trips.trend.168, col ="red", lwd = 2)
    
  #Decompose  
    #Daily
    ts.24 <- ts(Trip_hourly[,4], frequency = 24)
    D.a.ts.24 <- decompose(ts.24, "additive")
    D.m.ts.24 <- decompose(ts.24, "multiplicative")  
    
      #Additive
      plot(as.ts(D.a.ts.24$seasonal))
      plot(as.ts(D.a.ts.24$trend))
      plot(as.ts(D.a.ts.24$random))
      plot(D.a.ts.24)
    
      #multiplicative
      plot(as.ts(D.m.ts.24$seasonal))
      plot(as.ts(D.m.ts.24$trend))
      plot(as.ts(D.m.ts.24$random))
      plot(D.m.ts.24)
    
    #Weekly
    ts.168 <- ts(Trip_hourly[,4], frequency = 168)
    
      #Additive
        D.m.ts.24 <- ts.24 %>% decompose(type="additive")  %>%  autoplot() + xlab("Time") +
                      ggtitle("Classical Additive Decomposition of RideAustin Trip Counts")
        ggsave("D.m.ts.168.png", height = 6,  width = 6.25)
      
      #Multiplicative
        D.m.ts.168 <- ts.168 %>% decompose(type="multiplicative")  %>%  autoplot() + xlab("Time") +
                      ggtitle("Classical Multiplicative Decomposition of RideAustin Trip Counts")
        ggsave("D.m.ts.168.png", height = 6,  width = 6.25)
      
  #ACF and PACF Plots
  png("ACFpolt_trip_H.png")
  op <- par(mfrow=c(1,2))
  acf(trip_H, lag.max = 30, main = "RideAustin Time Series ACFs")
  acf(trip_H, lag.max = 175, main ="")
  par(op)
  dev.off()
  
  #QQ plot
  png("qqpolt_trip_H.png")
  qqnorm(trip_H)
  abline(0,1)
  dev.off()
```

$\mu = `r ts_mean`$

$\sigma^2 = `r ts_var`$

##Differencing
### d(1) Hour Differencing
```{r diff-1, echo=FALSE}
#24 Hour differencing
  trip_H.d.1 <- diff(trip_H, 1)
  
  #Time Series Stats
  ##png("tspolt_trip_H.d.24.png") 
  plot.ts(trip_H.d.1, xlab = "Hour", ylab = "Trip Count", main = "Hourly Trips provided by RideAustin d(1)")
  ##dev.off()
  
  #Summary Stats
  ts.d.1_mean <- mean(trip_H.d.1) 
  ts.d.1_var <- var(trip_H.d.1)
  
  #ACF and PACF Plots
  ##png("ACFpolt_trip_H.d.24.png")
  op <- par(mfrow=c(1,2))
  acf(trip_H.d.1, lag.max = 175)
  pacf(trip_H.d.1, lag.max = 175)
  par(op)
  ##dev.off()
  
  #QQ plot
  ##png("qqpolt_trip_H.d.24.png")
  qqnorm(trip_H.d.1)
  abline(0,1)
  ##dev.off()
```

$\mu = `r ts.d.1_mean`$

$\sigma^2 = `r ts.d.1_var`$

### D(24) Hour Differencing
```{r diff-24, echo=FALSE}
#24 Hour differencing
  trip_H.d.24 <- diff(trip_H, lag = 24, differences = 1)
  
  #Time Series Stats
  ##png("tspolt_trip_H.d.24.png") 
  plot.ts(trip_H.d.24, xlab = "Hour", ylab = "Trip Count", main = "Hourly Trips provided by RideAustin D(24)")
  ##dev.off()
  
  #Summary Stats
  ts.d.24_mean <- mean(trip_H.d.24) 
  ts.d.24_var <- var(trip_H.d.24)
  
  #ACF and PACF Plots
  ##png("ACFpolt_trip_H.d.24.png")
  op <- par(mfrow=c(1,2))
  acf(trip_H.d.24, lag.max = 175)
  pacf(trip_H.d.24, lag.max = 175)
  par(op)
  ##dev.off()
  
  #QQ plot
  ##png("qqpolt_trip_H.d.24.png")
  qqnorm(trip_H.d.24)
  abline(0,1)
  ##dev.off()
```

$\mu = `r ts.d.24_mean`$

$\sigma^2 = `r ts.d.24_var`$

### D(168) Hour Differencing
```{r diff-168, echo=FALSE}
#168 Hour differencing
  trip_H.d.168 <- diff(trip_H,lag = 168, differences = 1) #Note 24 hours between days and 168 hours between weeks (same hour)
  
  #Time Series Stats
  ##png("tspolt_trip_H.d.168.png") 
  plot.ts(trip_H.d.168, xlab = "Hour", ylab = "Trip Count", main = "Hourly Trips provided by RideAustin D(168)")
  ##dev.off()
  
  #Summary Stats
  ts.d.168_mean <- mean(trip_H.d.168) 
  ts.d.168_var <- var(trip_H.d.168)
  
  #ACF and PACF Plots
  ##png("ACFpolt_trip_H.d.168.png")
  op <- par(mfrow=c(1,2))
  acf(trip_H.d.168, lag.max = 175)
  pacf(trip_H.d.168, lag.max = 175)
  par(op)
  ##dev.off()
  
  #QQ plot
  ##png("qqpolt_trip_H.d.168.png")
  qqnorm(trip_H.d.168)
  abline(0,1)
  ##dev.off()
```

$\mu = `r ts.d.168_mean`$

$\sigma^2 = `r ts.d.168_var`$

### D(24,168) hour differencing
```{r diff-24-168, echo=FALSE}
#24 and 168 hour differencing
  trip_H.d.24.168 <- diff(trip_H.d.24, lag = 168, differences = 1)
  
  #Time Series Stats
  ##png("tspolt_trip_H.d.24.168.png") 
  plot.ts(trip_H.d.24.168, xlab = "Hour", ylab = "Trip Count", main = "Hourly Trips provided by RideAustin D(24,168)")
  ##dev.off()
  
  #Summary Stats
  ts.d.24.168_mean <- mean(trip_H.d.24.168) 
  ts.d.24.168_var <- var(trip_H.d.24.168)
  
  #ACF and PACF Plots
  ##png("ACFpolt_trip_H.d.24.168.png")
  op <- par(mfrow=c(1,2))
  acf(trip_H.d.24.168, lag.max = 175)
  pacf(trip_H.d.24.168, lag.max = 175)
  par(op)
  ##dev.off()
  
  #QQ plot
  ##png("qqpolt_trip_H.d.24.168.png")
  qqnorm(trip_H.d.24.168)
  abline(0,1)
  ##dev.off()
```

$\mu = `r ts.d.24.168_mean`$

$\sigma^2 = `r ts.d.24.168_var`$

### d(1) and D(168) hour differencing
```{r diff-1-168, echo=FALSE}
#d(1) and d(168) hour differencing
  trip_H.d.1.D.168 <- diff(diff(trip_H, 1), lag = 168, differences = 1)
  
  #Time Series Stats
  png("tspolt_trip_H.d.1.D.168.png") 
  plot.ts(trip_H.d.1.D.168, xlab = "Hour", ylab = expression(nabla~nabla[168]~X[t]), main = expression(nabla~nabla[168]~"Transformed Trip Count Data"))
  dev.off()
  
  #Summary Stats
  ts.d.1.168_mean <- mean(trip_H.d.1.168) 
  ts.d.1.168_var <- var(trip_H.d.1.168)
  
  #ACF and PACF Plots
  ##png("ACFpolt_trip_H.d.24.168.png")
  op <- par(mfrow=c(1,2))
  acf(trip_H.d.1.168, lag.max = 175)
  pacf(trip_H.d.1.168, lag.max = 175)
  par(op)
  ##dev.off()
  
  #QQ plot
  ##png("qqpolt_trip_H.d.24.168.png")
  qqnorm(trip_H.d.1.168)
  abline(0,1)
  ##dev.off()
```

$\mu = `r ts.d.1.168_mean`$

$\sigma^2 = `r ts.d.1.168_var`$

### d(1) and D(24) hour differencing
```{r diff-1-24, echo=FALSE}
#d(1) and d(24) hour differencing
  trip_H.d.1.24 <- diff(diff(trip_H, 1), lag = 24, differences = 1)
  
  #Time Series Stats
  ##png("tspolt_trip_H.d.24.168.png") 
  plot.ts(trip_H.d.1.24, xlab = "Hour", ylab = "Trip Count", main = "Hourly Trips provided by RideAustin d(1) & D(24)")
  ##dev.off()
  
  #Summary Stats
  ts.d.1.24_mean <- mean(trip_H.d.1.24) 
  ts.d.1.24_var <- var(trip_H.d.1.24)
  
  #ACF and PACF Plots
  ##png("ACFpolt_trip_H.d.24.168.png")
  op <- par(mfrow=c(1,2))
  acf(trip_H.d.1.24, lag.max = 175)
  pacf(trip_H.d.1.24, lag.max = 175)
  par(op)
  ##dev.off()
  
  #QQ plot
  ##png("qqpolt_trip_H.d.24.168.png")
  qqnorm(trip_H.d.1.24)
  abline(0,1)
  ##dev.off()
```

$\mu = `r ts.d.1.24_mean`$

$\sigma^2 = `r ts.d.1.24_var`$

### d(1) and D(24,168) hour differencing
```{r diff-1-24-168, echo=FALSE}
#d(1) and D(24,168) hour differencing
  trip_H.d.1.24.168 <- diff(diff(diff(trip_H, 1), lag = 24, differences = 1), lag =168, differences = 1)
  
  #Time Series Stats
  ##png("tspolt_trip_H.d.24.168.png") 
  plot.ts(trip_H.d.1.24.168, xlab = "Hour", ylab = "Trip Count", main = "Hourly Trips provided by RideAustin d(1) & D(24,168)")
  ##dev.off()
  
  #Summary Stats
  ts.d.1.24.168_mean <- mean(trip_H.d.1.24.168) 
  ts.d.1.24.168_var <- var(trip_H.d.1.24.168)
  
  #ACF and PACF Plots
  ##png("ACFpolt_trip_H.d.24.168.png")
  op <- par(mfrow=c(1,2))
  acf(trip_H.d.1.24.168, lag.max = 175)
  pacf(trip_H.d.1.24.168, lag.max = 175)
  par(op)
  ##dev.off()
  
  #QQ plot
  ##png("qqpolt_trip_H.d.24.168.png")
  qqnorm(trip_H.d.1.24.168)
  abline(0,1)
  ##dev.off()
```

$\mu = `r ts.d.1.24.168_mean`$

$\sigma^2 = `r ts.d.1.24.168_var`$

### d(1,24) and D(168) hour differencing
```{r diff-1-24-168a, echo=FALSE}
#d(1,24) and d(168) hour differencing
  trip_H.d.1.24.168a <- diff(diff(diff(trip_H, 1), 24), lag =168, differences = 1)
  
  #Time Series Stats
  ##png("tspolt_trip_H.d.24.168.png") 
  plot.ts(trip_H.d.1.24.168a, xlab = "Hour", ylab = "Trip Count", main = "Hourly Trips provided by RideAustin d(1,24) & D(168)")
  ##dev.off()
  
  #Summary Stats
  ts.d.1.24.168a_mean <- mean(trip_H.d.1.24.168a) 
  ts.d.1.24.168a_var <- var(trip_H.d.1.24.168a)
  
  #ACF and PACF Plots
  ##png("ACFpolt_trip_H.d.24.168.png")
  op <- par(mfrow=c(1,2))
  acf(trip_H.d.1.24.168a, lag.max = 175)
  pacf(trip_H.d.1.24.168a, lag.max = 175)
  par(op)
  ##dev.off()
  
  #QQ plot
  ##png("qqpolt_trip_H.d.24.168.png")
  qqnorm(trip_H.d.1.24.168a)
  abline(0,1)
  ##dev.off()
```

$\mu = `r ts.d.1.24.168a_mean`$

$\sigma^2 = `r ts.d.1.24.168a_var`$

### d(1,12) and D(168) hour differencing
```{r diff-1-12-168, echo=FALSE}
#d(1,12) and d(168) hour differencing
  trip_H.d.1.12.168 <- diff(diff(diff(trip_H, 1),12), lag = 168, differences = 1)
  
  #Time Series Stats
  ##png("tspolt_trip_H.d.24.168.png") 
  plot.ts(trip_H.d.1.12.168, xlab = "Hour", ylab = "Trip Count", main = "Hourly Trips provided by RideAustin d(1,12) & D(168)")
  ##dev.off()
  
  #Summary Stats
  ts.d.1.12.168_mean <- mean(trip_H.d.1.12.168) 
  ts.d.1.12.168_var <- var(trip_H.d.1.12.168)
  
  #ACF and PACF Plots
  ##png("ACFpolt_trip_H.d.24.168.png")
  op <- par(mfrow=c(1,2))
  acf(trip_H.d.1.12.168, lag.max = 175)
  pacf(trip_H.d.1.12.168, lag.max = 175)
  par(op)
  ##dev.off()
  
  #QQ plot
  ##png("qqpolt_trip_H.d.24.168.png")
  qqnorm(trip_H.d.1.12.168)
  abline(0,1)
  ##dev.off()
```

$\mu = `r ts.d.1.12.168_mean`$

$\sigma^2 = `r ts.d.1.12.168_var`$

##Transformations
###Box-Cox Transformation (lambda = 0.23)
```{r boxcox, echo=FALSE}
#Find parameter
  tc.bc <- powerTransform(trip_H ~ 1, family="yjPower")
  summary(tc.bc)

#Apply Transformation
  trip_H.t <- (trip_H)^(0.23)
  
#Time Series Stats
  ##png("tspolt_trip_H.t.png") 
  plot.ts(trip_H.t, xlab = "Hour", ylab = "BOXCOX(Trip Count)", main = "Hourly Trips provided by RideAustin")
  ##dev.off()
  
  #Summary Stats
  ts.t_mean <- mean(trip_H.t)
  ts.t_var <- var(trip_H.t)

  #ACF and PACF Plots
  ##png("ACFpolt_trip_H.t.png")
  op <- par(mfrow=c(1,2))
  acf(trip_H.t, lag.max = 350)
  pacf(trip_H.t, lag.max = 350)
  par(op)
  ##dev.off()

  #QQ plot
  ##png("qqpolt_trip_H.t.png")
  qqnorm(trip_H.t)
  abline(0,1)
 ## dev.off()
```

##Differencing
```{r differencing}
#Apply Differencing
  #d(1)
  trip_H.t.d.1 <- diff(trip_H.t,1)
  trip_H.t.d.6 <- diff(trip_H.t,6)
  trip_H.t.d.12 <- diff(trip_H.t,12)
  trip_H.t.d.24 <- diff(trip_H.t,24)
  trip_H.t.d.168 <- diff(trip_H.t,168)
  
  #d(1) & D(1)
  trip_H.t.d.1.D.6 <- diff(diff(trip_H.t,1),lag =  6, differences = 1)
  trip_H.t.d.1.D.12 <- diff(diff(trip_H.t,1),lag =  12, differences = 1)
  trip_H.t.d.1.D.24 <- diff(diff(trip_H.t,1),lag =  24, differences = 1)
  trip_H.t.d.1.D.168 <- diff(diff(trip_H.t,1),lag =  168, differences = 1)
  trip_H.t.d.6.D.12 <- diff(diff(trip_H.t,6),lag =  12, differences = 1)
  trip_H.t.d.6.D.24 <- diff(diff(trip_H.t,6),lag =  24, differences = 1)
  trip_H.t.d.6.D.168 <- diff(diff(trip_H.t,6),lag =  168, differences = 1)
  trip_H.t.d.12.D.24 <- diff(diff(trip_H.t,12),lag =  24, differences = 1)
  trip_H.t.d.12.D.168 <- diff(diff(trip_H.t,12),lag =  168, differences = 1)
  trip_H.t.d.24.D.168 <- diff(diff(trip_H.t,24),lag =  168, differences = 1)
  trip_H.t.d.168.D.12 <- diff(diff(trip_H.t,168),lag =  12, differences = 1)
  trip_H.t.d.168.D.24 <- diff(diff(trip_H.t,168),lag =  24, differences = 1)
  
  #d(1) & D(2)
  trip_H.t.d.1.D.6.12 <- diff(diff(diff(trip_H.t,1), lag = 6, differences = 1), lag = 12, differences = 1)
  trip_H.t.d.1.D.6.24 <- diff(diff(diff(trip_H.t,1), lag = 6, differences = 1), lag = 24, differences = 1)
  trip_H.t.d.1.D.6.168 <- diff(diff(diff(trip_H.t,1), lag = 6, differences = 1), lag = 168, differences = 1)
  trip_H.t.d.1.D.12.24 <- diff(diff(diff(trip_H.t,1), lag = 12, differences = 1), lag = 24, differences = 1)
  trip_H.t.d.1.D.12.168 <- diff(diff(diff(trip_H.t,1), lag = 12, differences = 1), lag = 168, differences = 1)
  trip_H.t.d.1.D.24.168 <- diff(diff(diff(trip_H.t,1), lag = 24, differences = 1), lag = 168, differences = 1)
  trip_H.t.d.6.D.12.24 <- diff(diff(diff(trip_H.t,6), lag = 12, differences = 1), lag = 24, differences = 1)
  trip_H.t.d.6.D.12.168 <- diff(diff(diff(trip_H.t,6), lag = 12, differences = 1), lag = 168, differences = 1)
  trip_H.t.d.6.D.24.168 <- diff(diff(diff(trip_H.t,6), lag = 24, differences = 1), lag = 168, differences = 1)
  trip_H.t.d.12.D.24.168 <- diff(diff(diff(trip_H.t,12), lag = 24, differences = 1), lag = 168, differences = 1)
  trip_H.t.d.24.D.12.168 <- diff(diff(diff(trip_H.t,24), lag = 12, differences = 1), lag = 168, differences = 1)
  trip_H.t.d.168.D.12.24 <- diff(diff(diff(trip_H.t,168), lag = 12, differences = 1), lag = 24, differences = 1)
  
  #d(1) & D(3)
  trip_H.t.d.1.D.6.12.24 <- diff(diff(diff(diff(trip_H.t,1), lag = 6, differences = 1), lag = 12, differences = 1),lag = 24, differences = 1)
  trip_H.t.d.1.D.6.12.168 <- diff(diff(diff(diff(trip_H.t,1), lag = 6, differences = 1), lag = 12, differences = 1),lag = 168, differences = 1)
  trip_H.t.d.1.D.6.24.168 <- diff(diff(diff(diff(trip_H.t,1), lag = 6, differences = 1), lag = 24, differences = 1),lag = 168, differences = 1)
  trip_H.t.d.1.D.12.24.168 <- diff(diff(diff(diff(trip_H.t,1), lag = 12, differences = 1), lag = 24, differences = 1),lag = 168, differences = 1)
  trip_H.t.d.6.D.12.24.168 <- diff(diff(diff(diff(trip_H.t,6), lag = 12, differences = 1), lag = 24, differences = 1),lag = 168, differences = 1)
  
  #d(2) - 10
  trip_H.t.d.1.6 <- diff(diff(trip_H.t,1),6)
  trip_H.t.d.1.12 <- diff(diff(trip_H.t,1),12)
  trip_H.t.d.1.24 <- diff(diff(trip_H.t,1),24)
  trip_H.t.d.1.168 <- diff(diff(trip_H.t,1),168)
  trip_H.t.d.6.12 <- diff(diff(trip_H.t,6),12)
  trip_H.t.d.6.24 <- diff(diff(trip_H.t,6),24)
  trip_H.t.d.6.168 <- diff(diff(trip_H.t,6),168)
  trip_H.t.d.12.24 <- diff(diff(trip_H.t,12),24)
  trip_H.t.d.12.168 <- diff(diff(trip_H.t,12),168)
  trip_H.t.d.24.168 <- diff(diff(trip_H.t,24),168)
  
  
  #d(2) & D(1)
  trip_H.t.d.1.6.D.12 <- diff(diff(diff(trip_H.t,1),6), lag = 12, differences = 1)
  trip_H.t.d.1.6.D.24 <- diff(diff(diff(trip_H.t,1),6), lag = 24, differences = 1)
  trip_H.t.d.1.6.D.168 <- diff(diff(diff(trip_H.t,1),6), lag = 168, differences = 1)
  trip_H.t.d.1.12.D.24 <- diff(diff(diff(trip_H.t,1),12), lag = 24, differences = 1)
  trip_H.t.d.1.12.D.168 <- diff(diff(diff(trip_H.t,1),12), lag = 168, differences = 1)
  trip_H.t.d.1.24.D.12 <- diff(diff(diff(trip_H.t,1),24), lag = 12, differences = 1)
  trip_H.t.d.1.24.D.168 <- diff(diff(diff(trip_H.t,1),24), lag = 168, differences = 1)
  trip_H.t.d.1.168.D.12 <- diff(diff(diff(trip_H.t,1),168), lag = 12, differences = 1)
  trip_H.t.d.1.168.D.24 <- diff(diff(diff(trip_H.t,1),168), lag = 24, differences = 1)
  
  #d(2) & D(2)
  trip_H.t.d.1.6.D.12.24 <- diff(diff(diff(diff(trip_H.t,1),6), lag = 12, differences = 1), lag = 24, differences = 1)
  trip_H.t.d.1.6.D.12.168 <- diff(diff(diff(diff(trip_H.t,1),6), lag = 12, differences = 1), lag = 168, differences = 1)
  trip_H.t.d.1.6.D.24.168 <- diff(diff(diff(diff(trip_H.t,1),6), lag = 24, differences = 1), lag = 168, differences = 1)
  trip_H.t.d.1.12.D.24.168 <- diff(diff(diff(diff(trip_H.t,1),12), lag = 24, differences = 1), lag = 168, differences = 1)
  trip_H.t.d.1.24.D.12.168 <- diff(diff(diff(diff(trip_H.t,1),24), lag = 12, differences = 1), lag = 168, differences = 1)
  trip_H.t.d.1.168.D.12.24 <- diff(diff(diff(diff(trip_H.t,1),168), lag = 12, differences = 1), lag = 24, differences = 1)
  
  #d(2) & D(3)
  trip_H.t.d.1.6.D.12.24.168 <- diff(diff(diff(diff(diff(trip_H.t,1),6), lag = 12, differences = 1), lag = 24, differences = 1), lag = 168, differences = 1)
  
  #d(3) & D(1)
  trip_H.t.d.1.6.12.D.24 <- diff(diff(diff(diff(trip_H.t,1),6),12), lag = 24, differences = 1)
  trip_H.t.d.1.6.12.D.168 <- diff(diff(diff(diff(trip_H.t,1),6),12), lag = 168, differences = 1)
  trip_H.t.d.1.12.24.D.168 <- diff(diff(diff(diff(trip_H.t,1),12),24), lag = 168, differences = 1)
  trip_H.t.d.1.12.168.D.24 <- diff(diff(diff(diff(trip_H.t,1),12),168), lag = 24, differences = 1)
  trip_H.t.d.1.24.168.D.12 <- diff(diff(diff(diff(trip_H.t,1),24),168), lag = 12, differences = 1)
  
  #d(3) & D(2)
  trip_H.t.d.1.6.12.D.12.24 <- diff(diff(diff(diff(diff(trip_H.t,1),6),12), lag = 12, differences = 1), lag = 24, differences = 1)
  trip_H.t.d.1.6.12.D.24.168 <- diff(diff(diff(diff(diff(trip_H.t,1),6),12), lag = 24, differences = 1), lag = 168, differences = 1)
  trip_H.t.d.1.6.24.D.12.24 <- diff(diff(diff(diff(diff(trip_H.t,1),6),24), lag = 12, differences = 1), lag = 24, differences = 1)
  trip_H.t.d.1.6.24.D.12.168 <- diff(diff(diff(diff(diff(trip_H.t,1),6),24), lag = 12, differences = 1), lag = 168, differences = 1)
  trip_H.t.d.1.6.168.D.12.24 <- diff(diff(diff(diff(diff(trip_H.t,1),6),168), lag = 12, differences = 1), lag = 24, differences = 1)
 
#Summary Stats  
 #d(1) -5
  ts.t.d.1_var <- var(trip_H.t.d.1)
  ts.t.d.6_var <- var(trip_H.t.d.6)
  ts.t.d.12_var <- var(trip_H.t.d.12)
  ts.t.d.24_var <- var(trip_H.t.d.24)
  ts.t.d.168_var <- var(trip_H.t.d.168)
  
  #d(1) & D(1) - 13
  ts.t.d.1.D.6_var <- var(trip_H.t.d.1.D.6)
  ts.t.d.1.D.12_var <- var(trip_H.t.d.1.D.12)
  ts.t.d.1.D.24_var <- var(trip_H.t.d.1.D.24)
  ts.t.d.1.D.168_var <- var(trip_H.t.d.1.D.168)
  ts.t.d.6.D.12_var <- var(trip_H.t.d.1.D.12)
  ts.t.d.6.D.24_var <- var(trip_H.t.d.1.D.24)
  ts.t.d.6.D.168_var <- var(trip_H.t.d.1.D.168)
  ts.t.d.12.D.24_var <- var(trip_H.t.d.1.D.24)
  ts.t.d.12.D.168_var <- var(trip_H.t.d.1.D.168)
  ts.t.d.24.D.12_var <- var(trip_H.t.d.1.D.12)
  ts.t.d.24.D.168_var <- var(trip_H.t.d.1.D.168)
  ts.t.d.168.D.12_var <- var(trip_H.t.d.1.D.12)
  ts.t.d.168.D.24_var <- var(trip_H.t.d.1.D.24)
  
  #d(1) & D(2) - 12
  ts.t.d.1.D.6.12_var <- var(trip_H.t.d.1.D.6.12)
  ts.t.d.1.D.6.24_var <- var(trip_H.t.d.1.D.6.24)
  ts.t.d.1.D.6.168_var <- var(trip_H.t.d.1.D.6.168)
  ts.t.d.1.D.12.24_var <- var(trip_H.t.d.1.D.12.24)
  ts.t.d.1.D.12.168_var <- var(trip_H.t.d.1.D.12.168)
  ts.t.d.1.D.24.168_var <- var(trip_H.t.d.1.D.24.168)
  ts.t.d.6.D.12.24_var <- var(trip_H.t.d.6.D.12.24)
  ts.t.d.6.D.12.168_var <- var(trip_H.t.d.6.D.12.168)
  ts.t.d.6.D.24.168_var <- var(trip_H.t.d.6.D.24.168)
  ts.t.d.12.D.24.168_var <- var(trip_H.t.d.12.D.24.168)
  ts.t.d.24.D.12.168_var <- var(trip_H.t.d.24.D.12.168)
  ts.t.d.168.D.12.24_var <- var(trip_H.t.d.168.D.12.24)
  
  #d(1) & D(3) - 5
  ts.t.d.1.D.6.12.24_var <- var(trip_H.t.d.1.D.6.12.24)
  ts.t.d.1.D.6.12.168_var <- var(trip_H.t.d.1.D.6.12.168)
  ts.t.d.1.D.6.24.168_var <- var(trip_H.t.d.1.D.6.24.168)
  ts.t.d.1.D.12.24.168_var <- var(trip_H.t.d.1.D.12.24.168)
  ts.t.d.6.D.12.24.168_var <- var(trip_H.t.d.6.D.12.24.168)
  
  #d(2)
  ts.t.d.1.6_var <- var(trip_H.t.d.1.6) 
  ts.t.d.1.12_var <- var(trip_H.t.d.1.12) 
  ts.t.d.1.24_var <- var(trip_H.t.d.1.24)
  ts.t.d.1.168_var <- var(trip_H.t.d.1.168)
  ts.t.d.6.12_var <- var(trip_H.t.d.6.12) 
  ts.t.d.6.24_var <- var(trip_H.t.d.6.24)
  ts.t.d.6.168_var <- var(trip_H.t.d.6.168) 
  ts.t.d.12.24_var <- var(trip_H.t.d.12.24) 
  ts.t.d.12.168_var <- var(trip_H.t.d.12.168) 
  ts.t.d.24.168_var <- var(trip_H.t.d.24.168) 
  
  #d(2) & D(1)
  ts.t.d.1.6.D.12 <- var(trip_H.t.d.1.6.D.12) 
  ts.t.d.1.6.D.24 <- var(trip_H.t.d.1.6.D.24) 
  ts.t.d.1.6.D.168 <- var(trip_H.t.d.1.6.D.168)
  ts.t.d.1.12.D.24 <- var(trip_H.t.d.1.12.D.24) 
  ts.t.d.1.12.D.168 <- var(trip_H.t.d.1.12.D.168) 
  ts.t.d.1.24.D.12 <- var(trip_H.t.d.1.24.D.12) 
  ts.t.d.1.24.D.168 <- var(trip_H.t.d.1.24.D.168)
  ts.t.d.1.168.D.12 <- var(trip_H.t.d.1.168.D.12)
  ts.t.d.1.168.D.24 <- var(trip_H.t.d.1.168.D.24) 
  
  #d(2) & D(2)
  var(trip_H.t.d.1.6.D.12.24) 
  var(trip_H.t.d.1.6.D.12.168) 
  var(trip_H.t.d.1.6.D.24.168) 
  var(trip_H.t.d.1.12.D.24.168) 
  var(trip_H.t.d.1.24.D.12.168) 
  var(trip_H.t.d.1.168.D.12.24) 
  
  #d(2) & D(3)
  var(trip_H.t.d.1.6.D.12.24.168) 
  
  #d(3) & D(1)
  var(trip_H.t.d.1.6.12.D.24) 
  var(trip_H.t.d.1.6.12.D.168) 
  var(trip_H.t.d.1.12.24.D.168) 
  var(trip_H.t.d.1.12.168.D.24) 
  var(trip_H.t.d.1.24.168.D.12) 
  
  #d(3) & D(2)
  var(trip_H.t.d.1.6.12.D.12.24) 
  var(trip_H.t.d.1.6.12.D.24.168)
  var(trip_H.t.d.1.6.24.D.12.24) 
  var(trip_H.t.d.1.6.24.D.12.168) 
  var(trip_H.t.d.1.6.168.D.12.24)
```



Before Differencing:

$\mu = `r ts.t_mean`$

$\sigma^2 = `r ts.t_var`$

After Differencing with d(1) and D(168):

$\mu = `r ts.t.d.1.168_mean`$

$\sigma^2 = `r ts.t.d.1.168_var`$

##Examine Selected Time Series 
```{r ts-stats}
#Plots for Best TS
  #d(1)Time Series Plot
  png("tspolt_trip_H.t.d.1.png")
    plot(trip_H.t.d.1, xlab = "Hour", ylab="",main = expression(nabla~"Transformed Trip Count Data"))
    title(ylab = expression(nabla~X[t]^0.23), line = 2)
  dev.off()
  
  #d(1) & D(168) Time Series Plot
  png("tspolt_trip_H.t.d.1.D.168.png")
    plot(trip_H.t.d.1, xlab = "Hour", ylab="",main = expression(nabla~nabla[168]~"Transformed Trip Count Data"))
    title(ylab = expression(nabla~nabla[168]~X[t]^0.23), line = 2)
  dev.off()
  
#ACF and PACF Plots
  png("ACFpolt_trip_H.t.d.1.D.168.L.30.png")
  op <- par(mfrow=c(1,2))
  acf(trip_H.t.d.1.D.168, lag.max = 30, main="")
  pacf(trip_H.t.d.1.D.168, lag.max = 30,main="")
  mtext("Series ACF and PACF (lag = 30)", side = 3, line = -2, outer = TRUE, font = 2)
  par(op)
  dev.off()

  png("ACFpolt_trip_H.t.d.1.D.168.L.175.png")
  op <- par(mfrow=c(1,2))
  acf(trip_H.t.d.1.D.168, lag.max = 175, main="")
  pacf(trip_H.t.d.1.D.168, lag.max = 175,main="")
  mtext("Series ACF and PACF (lag = 175)", side = 3, line = -2, outer = TRUE, font = 2)
  par(op)
  dev.off()
  
  #QQ plot
  png("qqpolt_trip_H.t.d.24.168.png")
  qqnorm(trip_H.t.d.1.D.168)
  abline(0,1)
 dev.off()
  
##Check for Stationarity
  trip_H.t.d.1.D.168 %>% ur.kpss() %>% summary()
```

With KPSS test, $H_0 : the time series is stationary$. The test statistic indicates that it is unreasonable to reject the null hypothesis. 

#Model Identification
```{r ARMA-modelID}
#Auto.arima suggestion
  auto.arima(trip_H.t.d.1.D.168)

#Explore Parameter Range
  #ARMA Stats DF
  ARMA_summ <- tibble(p = 0, q=0, sigma2 = 0.00, na.se = 0, aic = 0.00, LL = 0.00, rss = 0.000)
  
  #Solve Models
  for(i in 1:12){
    for(j in 1:12){
      #Model
      ARMA_can <- arima(trip_H.t.d.1.D.168, order = c(i,0,j))
      
      #Update Summary
      ARMA_summ <- ARMA_summ %>% add_row(p = i, q = j, sigma2 = ARMA_can$sigma2, na.se = sum(is.na(sqrt(diag(ARMA_can$var.coef)))), aic = ARMA_can$aic, LL = ARMA_can$loglik, rss = sum((ARMA_can$residuals)^2))
    }
  }

  #Candidate ARMA Models
  ARMA_canmodels <- filter(ARMA_summ, aic <= 1430, p >0, na.se == 0)

#Save image
  save.image()
```

```{r SARIMA-modelID}
  #SARIMA Stats DF
  SARIMA_summ <- tibble(p = 0, q=0, P = 0, Q = 0, S = 0, sigma2 = 0.00, na.se = 0.00, aic = 0.00, LL = 0.00, rss = 0.000)
  SARIMA_models <- list()
  counter <- 1
  
  #Set seasons
  Seas <- c(6,12,24)
  
  for(i in 2:2){
    for(j in 0:6){
      for(m in 0:4){
        for(n in 0:4){
          for(k in 1:length(Seas)){
            print("");cat("Model"); cat(" p:"); cat(i); cat(" q:"); cat(j); cat(" P:"); cat(m); cat(" Q:"); cat(n); cat(" S:"); cat(Seas[k])
          #ARIMA
            ARIMA_v <- c(i,0,j)
            SARIMA_V <- c(m,0,n)
          
          #Model
            SARIMA_can <- sarima.can(trip_H.t.d.1.D.168, ARIMA_v, SARIMA_V, Seas[k])
            
          #If valid solution
            if(!is.na(SARIMA_can)){
              #Add to list
                SARIMA_models[[counter]] <- SARIMA_can
                
                
              #Update Summary
                SARIMA_summ <- SARIMA_summ %>% add_row(p = ARIMA_v[1], q = ARIMA_v[3], P = SARIMA_V[1], Q = SARIMA_V[3], S = Seas[k], sigma2 = SARIMA_can$sigma2, na.se = sum(is.na(sqrt(diag(SARIMA_can$var.coef)))), aic = SARIMA_can$aic, LL = SARIMA_can$loglik, rss = sum((SARIMA_can$residuals)^2))
            } else{
              SARIMA_summ <- SARIMA_summ %>% add_row(p = ARIMA_v[1], q = ARIMA_v[3], P = i, Q = j, S = Seas[k], sigma2 = NA, na.se = NA, aic = NA, LL = NA, rss = NA)
            }#End If
            
          #Increase counter
            counter <- counter + 1
            
          #Save output
            write.csv(SARIMA_summ, "SARIMA_summ.csv")
          }
        }
      }
    }
  }
  #Save and Output Data
  save.image()
  write.csv(SARIMA_summ, "SARIMA_summ.csv")
  
#Higher Order Models  
  for(i in 0:2){
    for(j in 0:2){
      for(k in 1:length(Seas)){
        for(l in 1:length(ARMA_canmodels$p)){
          print("");cat("Model"); cat(" p:"); cat(ARMA_canmodels$p[l]); cat(" q:"); cat(ARMA_canmodels$q[l]); cat(" P:"); cat(i); cat(" Q:"); cat(j); cat(" S:"); cat(Seas[k])
          #ARIMA
            ARIMA_v <- c(ARMA_canmodels$p[l],0,ARMA_canmodels$q[l])
            SARIMA_V <- c(i,0,j)
          
          #Model
            SARIMA_can <- sarima.can(trip_H.t.d.1.D.168, ARIMA_v, SARIMA_V, Seas[k])
            
          #If valid solution
            if(!is.na(SARIMA_can)){
              #Add to list
                SARIMA_models[[counter]] <- SARIMA_can
                
              #Update Summary
                SARIMA_summ <- SARIMA_summ %>% add_row(p = ARIMA_v[1], q = ARIMA_v[3], P = i, Q = j, S = Seas[k], sigma2 = SARIMA_can$sigma2, na.se = sum(is.na(sqrt(diag(SARIMA_can$var.coef)))), aic = SARIMA_can$aic, LL = SARIMA_can$loglik, rss = sum((SARIMA_can$residuals)^2))
            } else{
              SARIMA_summ <- SARIMA_summ %>% add_row(p = ARIMA_v[1], q = ARIMA_v[3], P = i, Q = j, S = Seas[k], sigma2 = NA, na.se = NA, aic = NA, LL = NA, rss = NA)
            }#End If
            
        #Increase counter
          counter <- counter + 1
        
        #Save output   
          write.csv(SARIMA_summ, "SARIMA_summC.csv")
        }
      }
    }
  }
  
  #Save and Output Data
  save.image()
  
```
auto.arima suggested a ARMA(2,0,2) model with sigma^2 estimated as 0.07151 and AIC=1480.13   AICc=1480.14   BIC=1514.65.

However, we found several models with higher orders with attractive properties.



